\section{Vectors}
\begin{frame}[fragile]{Vectors}
  \begin{itemize}
    \item Vectors live in a vector space.
    \item Most classes in \Queso\ are templated around vector implementation.
    \item The default vector/matrix implementation is \Gsl.
  \end{itemize}
  \begin{verbatim}
QUESO::VectorSpace<> paramSpace(env, "param_", 1, NULL);
  \end{verbatim}
  Arguments:
  \begin{itemize}
    \item The environment.
    \item The prefix for input file items.
    \item The dimension of the vector space.
    \item A pointer to a \texttt{std:vector} of \texttt{std:string}s for naming
      components of the vectors.  Good for `naming' parameters.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{Vectors}
  In \Queso\ \texttt{v0.53.x}, the following classes are equivalent:
  \begin{verbatim}
QUESO::VectorSpace<>
QUESO::VectorSpace<QUESO::GslVector, QUESO::GslMatrix>
  \end{verbatim}
  \begin{itemize}
    \item The default template type is
      \texttt{QUESO::GslVector}/\texttt{QUESO::GslMatrix}.
    \item The \Queso\ development team are working closely with the
      \texttt{DAKOTA} team at Sandia to provide a wider range of
      high-perfomance vector/matrix implementations in the 12--15 month
      timeline.
    \item If you really don't like \texttt{QUESO::} everywhere, you can
      insert
      \begin{verbatim}
using namespace QUESO;
      \end{verbatim}
       in your code and remove all instances of \texttt{QUESO::} elsewhere.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{Vectors}
  This \texttt{zeroVector} method returns a \texttt{GslVector} object belonging
  to the vector space with every component set to zero.
  \begin{verbatim}
paramSpace.zeroVector();
  \end{verbatim}
  Use the vector space to eke out the zero vector, then copy it.
  \begin{verbatim}
QUESO::GslVector myVector(paramSpace.zeroVector());
  \end{verbatim}
  Argument is another \texttt{GslVector} object.
\end{frame}

\begin{frame}[fragile]{Vectors}
  Set element \texttt{3}:
  \begin{verbatim}
myVector[2] = 1.0;
  \end{verbatim}
  Get element \texttt{2}:
  \begin{verbatim}
double myElement = myVector[1];
  \end{verbatim}
  Set every element to \texttt{5.0}:
  \begin{verbatim}
myVector.cwSet(5.0);
  \end{verbatim}
  For other methods, see \url{http://libqueso.com/queso/html/a00129.html}
\end{frame}
